Comparison of Catalogs

### 2024-09-27 compare/compare.qmd
created functions for completeness (plot and table of bins)

-   The data have been joined based on their position in the sky (Ra, Dec, Distance).
-   We use TOPCAT to create two joins, an inner and an outer join
-   We will use the inner join for 1-1 comparisons
-   If we see that the data are similar we can use the outer join
-   For the comparison we keep the parameters names exactly they are given in the catalogs

```{python}
#| echo: false
import numpy as np
import matplotlib.pyplot as plt
from sklearn.metrics import r2_score
from astropy.io import ascii
from astropy.coordinates import SkyCoord
from astropy.table import Table, join, QTable
import astropy.units as u
from astropy.visualization import quantity_support, hist
#quantity_support()
from astropy.stats import sigma_clip, SigmaClip
from astropy.modeling import models, fitting
from scipy.stats import pearsonr
import seaborn as sns
import pandas as pd
import glob
import os
plt.style.use('ggplot')
pd.set_option('display.float_format', lambda x: '%.f' % x)

dt = QTable(ascii.read("../tables/inner_join.ecsv"), masked=True)
```

The dataset we are going to use consists of `{python} len(dt)` galaxies and `{python} len(dt.colnames)` columns.

@@

    Returns:
    None. The function displays a scatter plot with a fitted linear model.
    """
    # Convert data to masked arrays, masking NaN values
    x_data = np.ma.array(x.value, mask=np.isnan(x.value))
    y_data =  np.ma.array(y.value, mask=np.isnan(y.value))

@@

    # Show the plot
    plt.show()
```

>>>>

-   The data have been joined based on their position in the sky (Ra, Dec).
    -   We assume that every galaxy within 2 arc seconds of the initial coordinates is the same galaxy.
-   We use TOPCAT to create two joins, an inner and an outer join
-   We will use the inner join for 1-1 comparisons
-   If we see that the data are similar we can use the outer join
-   For the comparison we keep the parameters names exactly they are given in the catalogs

```{python}
#| echo: false
import numpy as np
import matplotlib.pyplot as plt
from sklearn.metrics import r2_score
import astropy
from astropy.io import ascii
from astropy.coordinates import SkyCoord
from astropy.table import Table, join, QTable
import astropy.units as u
from astropy.visualization import quantity_support, hist
#quantity_support()
from astropy.stats import sigma_clip, SigmaClip
from astropy.modeling import models, fitting
from scipy.stats import pearsonr
import seaborn as sns
import pandas as pd
import glob
import os
from tabulate import tabulate
from IPython.display import Markdown, display

plt.style.use('ggplot')
pd.set_option('display.float_format', lambda x: '%.f' % x)

dt = QTable(ascii.read("../tables/inner_join.ecsv"), masked=True)

inner = dt
outer = QTable(ascii.read("../tables/outer_join.ecsv"), masked=True)
hec_not_lcv = QTable(ascii.read("../tables/HEC_not_LCV_join.ecsv"), masked=True)
lcv_not_hec = QTable(ascii.read("../tables/LCV_not_HEC_join.ecsv"), masked=True)

lcv = QTable(ascii.read("../tables/final_table.ecsv"), masked=True)
hec = QTable(ascii.read("../tables/HECATE_LCV.ecsv"), masked=True)
```

The dataset we are going to use for the comparison (inner join) consists of `{python} len(dt)` galaxies and `{python} len(dt.colnames)` columns.

# Catalog Completeness

Checking for completeness in galaxy catalogs is essential to ensure that the data accurately represents the true population of galaxies. Incomplete catalogs can lead to biased results in statistical studies, such as the distribution of galaxy luminosity, mass, or star formation rates. Additionally, missing galaxies, especially those at faint magnitudes or large distances, can distort cosmological measurements and hinder our understanding of galaxy formation and evolution.

Completeness checks are crucial for addressing selection biases, ensuring accurate redshift distributions, and validating galaxy simulations. They help identify gaps in the data and guide follow-up observations, ensuring that the catalog provides a reliable sample for scientific analysis. Without these checks, conclusions drawn from the data may be inaccurate or incomplete.

------------------------------------------------------------------------

Checking for completeness in galaxy catalogs is essential to ensure that the data accurately represents the true population of galaxies. Incomplete catalogs can lead to biased results in statistical studies, such as the distribution of galaxy luminosity, mass, or star formation rates. Additionally, missing galaxies, especially those at faint magnitudes or large distances, can distort cosmological measurements and hinder our understanding of galaxy formation and evolution. Completeness checks are crucial for addressing selection biases, ensuring accurate redshift distributions, and validating galaxy simulations.

Distance-based corrections are applied to mitigate these biases by adjusting for the underrepresentation of galaxies at greater distances. As galaxies move farther away, they become fainter and harder to detect, leading to a drop in the number of detected galaxies. Methods like **volume corrections** (e.g., V/Vmax) and **luminosity function-based corrections** help account for these effects by estimating the true galaxy population based on the observed sample. These corrections ensure that statistical analyses, even in incomplete catalogs, more accurately reflect the full galaxy population.

```{python}
#| output: asis
# Creating a dataframe with the lengths of each table
data = {
    "Table": ["Inner join", "Outer join", "LCV", "HECATE", "Unique galaxies in LCV", "Unique Galaxies in Hecate"],
    "Number of galaxies": [len(dt), len(outer), len(lcv), len(hec), len(lcv_not_hec), len(hec_not_lcv)]
}

df_lengths = pd.DataFrame(data)

# Pretty print the dataframe in markdown format
df_lengths_md = df_lengths.to_markdown(index=False)
print(df_lengths_md)

## Completeness of the Inner join

$$
\text{Completeness (X)}=\frac{\text{(Galaxies in Inner Join)}}{\text{(Galaxies in X)}}×100\%
$$

Completeness (HECATE)= `{python} round(len(dt)/len(hec) *100)` %

Completeness (LCV)= `{python} round(len(dt)/len(lcv) *100)` %

## Completeness in Outer join

$$
\text{Completeness (X)}=\frac{\text{(Galaxies in Outer Join form X)}}{\text{(Galaxies in X)}}×100\%
$$

Completeness (HECATE)= `{python} round(len(hec_not_lcv)/len(hec)*100)` %

Completeness (LCV)= `{python} round(len(lcv_not_hec)/len(lcv)*100)` %

Combined Completeness =$\frac{\text{Total galaxies in Outer}}{\text{Unique galaxies in HECATE + LCV}}$= `{python} round(len(outer)/(len(lcv_not_hec)+(len(hec_not_lcv))) * 100)` %

## Completeness of the Data

```{python}
def plot_completeness(dataset_choice="lcv", column_name="Dis", description="Distance", units=True, logx=False, logy=False, bins=0, keep_nan=False):
    """
    Plots histograms with KDE and displays a table of counts and percentages for each bin, 
    based on the choice of dataset (LCV or HEC).

    Parameters:
    - dataset_choice: A string indicating which dataset to use ("lcv" or "hec")
    - column_name: The column name in the Qtable to plot and analyze (default is "Dis")
    - description: What to show in the title and the axis (default "Distance")
    - units: Show units or not (default is True)
    - logx: logarithmic x-axis (default is False)
    - logy: logarithmic y-axis (default is False)
    - bins: Number of bins or custom bin edges (default is 'auto')
    - keep_nan: keep (True) or remove NaN's (default is True)
    """

    if dataset_choice == "lcv":
        main_df, unique_df, label = lcv, lcv_not_hec, "LCV"
    elif dataset_choice == "hec" and hec is not None and hec_not_lcv is not None:
        main_df, unique_df, label = hec, hec_not_lcv, "HECATE"
    else:
        raise ValueError("Invalid dataset choice. Please choose 'lcv' or 'hec' with valid datasets.")

# Remove NaN values and strip units before plotting
    if not keep_nan:
        main_data_clean = main_df[column_name].value.filled(np.nan)
        main_data_clean = main_data_clean[~np.isnan(main_data_clean)]

        unique_data_clean = unique_df[column_name].value.filled(np.nan)
        unique_data_clean = unique_data_clean[~np.isnan(unique_data_clean)]
    else:
        main_data_clean = main_df[column_name].value.filled(np.nan)
        unique_data_clean = unique_df[column_name].value.filled(np.nan)

    # Check if bins is an integer or array of bin edges
    if bins == 0:
        counts, bin_edges = np.histogram(main_data_clean, bins='auto')
    elif isinstance(bins, int):
        counts, bin_edges = np.histogram(main_data_clean, bins=bins)
    else:
        bin_edges = bins  # If bins is an array of bin edges

    # Plot the histograms
    sns.histplot(main_data_clean.data, bins=bin_edges, kde=True, label=label)
    sns.histplot(unique_data_clean.data, bins=bin_edges, kde=True, label=f"Unique for {label}")

    # Set logarithmic axes if requested
    if logx:
        plt.xscale('log')
    if logy:
        plt.yscale('log')

    # Set the title and labels
    plt.title(f"Completeness of {description} for {label}")
    if units and main_df[column_name].unit is not None:
        plt.xlabel(f"{description} [{main_df[column_name].unit}]")
    else:
        plt.xlabel(f"{description}")
    plt.ylabel("Number of galaxies")
    plt.legend()

    # Calculate histogram counts for each dataset
    main_counts, _ = np.histogram(main_data_clean, bins=bin_edges)
    unique_counts, _ = np.histogram(unique_data_clean, bins=bin_edges)

    # Calculate bin centers for annotation
    bin_centers = 0.5 * (bin_edges[1:] + bin_edges[:-1])

    # Annotate percentages on the bars
    for i, center in enumerate(bin_centers):
        if main_counts[i] > 0:
            unique_pct = (unique_counts[i] / main_counts[i]) * 100
            plt.text(center, unique_counts[i], f'{unique_pct:.1f}%', color="green", ha='center', va='bottom')

    # Show the plot
    plt.show()
    plt.close()

```{python}
def table_completeness(dataset_choice, column_name="Dis", description = "Distance", keep_nan = False):
    """
    Creates a table of counts and percentages for each bin based on the chosen dataset (LCV or HEC).

    Parameters:
    - dataset_choice: A string indicating which dataset to use ("lcv" or "hec")
    - column_name: The column name in the datasets to analyze (default is "Dis")
    - description: what to show in the title and the axis (default "Distance")
    """

    if dataset_choice == "lcv":
        main_df, unique_df, label = lcv, lcv_not_hec, "LCV"
    elif dataset_choice == "hec" and hec is not None and hec_not_lcv is not None:
        main_df, unique_df, label = hec, hec_not_lcv, "HEC"
    else:
        raise ValueError("Invalid dataset choice. Please choose 'lcv' or 'hec' with valid datasets.")

    # Remove NaN values before plotting
    if keep_nan == False:
        main_df = main_df[~np.isnan(main_df[column_name].data)]
        unique_df = unique_df[~np.isnan(unique_df[column_name].data)]
    else:
        main_df = main_df[column_name].data
        unique_dF = unique_df[column_name].data
    counts, bin_edges = np.histogram(main_df[column_name].data, bins='auto')

    main_counts, _ = np.histogram(main_df[column_name].data, bins=bin_edges)
    unique_counts, _ = np.histogram(unique_df[column_name].data, bins=bin_edges)
    inner_counts, _ = np.histogram(inner[column_name].data, bins=bin_edges)

    bin_centers = 0.5 * (bin_edges[1:] + bin_edges[:-1])
    table_data = []

    for i in range(len(bin_centers)):
        if main_counts[i] > 0:
            unique_pct = (unique_counts[i] / main_counts[i]) * 100
            inner_pct = (inner_counts[i] / main_counts[i]) * 100
            table_data.append({
                "Bin Start": round(bin_edges[i]),
                "Bin End": round(bin_edges[i+1]),
                f"Unique %": f'{unique_pct:.0f}%',
                "Inner %": f'{inner_pct:.0f}%'
            })
    table_df = pd.DataFrame(table_data)
    return table_df
```

### Distance

```{python}
#| fig-cap: "Histograms showing the Distance Completeness of the Catalogs"
#| layout-ncol: 2
#| fig-subcap: 
#| - "HECATE"
#| - "LCV"
#| label: fig-dis-comp

plot_completeness("hec", column_name = "D", description = "Distance", keep_nan = True)
plot_completeness("lcv",keep_nan = True)
```
```{python}
#| label: tbl-dis-comp
#| tbl-cap: "Table showing the Completeness of the Catalogs, per bin"
#| layout-ncol: 2
#| tbl-subcap: 
#| - "HECATE"
#| - "LCV"
table_completeness("hec", column_name = "D", description = "Distance")

table_completeness("lcv")
```

### Type

```{python}
#| layout-ncol: 2
#| fig-cap: "Histograms showing the Type Completeness of the Catalogs"
#| fig-subcap: 
#| - "HECATE"
#| - "LCV"
#| label: fig-type-comp
plt.close()
plot_completeness("hec", column_name = "T", description = "Type", units = False)
plot_completeness("lcv", column_name = "TType", description = "Type", units = False, bins = 12)
```

As we can see from the histograms @fig-dis-comp and @fig-type-comp the sample of unique galaxies of each catalog, gets smaller by an almost constant proportion (Inner join).

This means there is no bias in the selection of the galaxies.

### Helocentric Radial Velocities

```{python}
#| layout-ncol: 2
#| fig-cap: "Histograms showing the Velocity Completeness of the Catalogs"
#| fig-subcap: 
#| - "HECATE"
#| - "LCV"
#| label: fig-type-comp
plt.close()
plot_completeness("hec", column_name = "V", description = "Velocities", keep_nan = True, logx = True)
plot_completeness("lcv", column_name = "RVel", description = "Velocities",keep_nan = True)
```

### Luminosities

```{python}
#| layout-ncol: 2
#| fig-cap: "Histograms showing the $L_K$ Completeness of the Catalogs"
#| fig-subcap: 
#| - "HECATE"
#| - "LCV"
#| label: fig-type-comp
plt.close()
plot_completeness("hec", column_name = "logL_K", description = "$log_{10}(L_K)$", units = False,keep_nan = False, bins = 0)
plot_completeness("lcv", column_name = "logKLum", description = "$log_{10}(L_K)$",units=False,keep_nan = False)
```

```{python}
# Plot the histograms
plt.close()
sns.histplot(hec_not_lcv["logL_K"], kde=True, label = "afd")
sns.histplot(hec["logL_K"], kde=True, label=f"Unique for")
plt.legend()
plt.show()
plt.close()
```

```{python}
sns.scatterplot(table_completeness("hec", "logL_K"),x = "Bin End", y = "Unique %")
plt.show()
```

### Magnitudes

### SFR

### Masses

@@

    Returns:
    None. The function displays a scatter plot with a fitted linear model.
    """
    plt.close()
    # Convert data to masked arrays, masking NaN values
    x_data = np.ma.array(x.value, mask=np.isnan(x.value))
    y_data =  np.ma.array(y.value, mask=np.isnan(y.value))

@@

    # Show the plot
    plt.show()
    plt.close()
```

### 2024-09-27 compare/compare.tex
created functions for completeness (plot and table of bins)

\caption{\label{fig-dis-comp}Histograms showing the Completeness of the
Catalogs}

@@

@@

\caption{\label{fig-type-comp}Histograms showing the Completeness of the
Catalogs}

\begin{longtable}[]{@{}rr@{}}
\toprule\noalign{}
Value & Count \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
-3 & 138 \\
-2 & 224 \\
-1 & 119 \\
0 & 4 \\
1 & 7 \\
2 & 2 \\
3 & 8 \\
4 & 9 \\
5 & 7 \\
6 & 24 \\
7 & 31 \\
8 & 86 \\
9 & 166 \\
10 & 484 \\
11 & 4 \\
\end{longtable}

\begin{longtable}[]{@{}rr@{}}
\toprule\noalign{}
Value & Count \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
-5 & 52 \\
-4.9 & 7 \\
-4.8 & 13 \\
-4.7 & 2 \\
-4.3 & 2 \\
-4 & 3 \\
-3.9 & 1 \\
-3.7 & 1 \\
-3.5 & 3 \\
-3.3 & 1 \\
-3.1 & 1 \\
-3 & 11 \\
-2.9 & 3 \\
-2.8 & 3 \\
-2.7 & 3 \\
-2.6 & 5 \\
-2.5 & 1 \\
-2.1 & 2 \\
-2 & 3 \\
-1.9 & 1 \\
-1.8 & 3 \\
-1.7 & 1 \\
-1.6 & 1 \\
-1.3 & 2 \\
-1 & 8 \\
-0.8 & 1 \\
-0.4 & 2 \\
-0.1 & 1 \\
0 & 3 \\
0.1 & 1 \\
0.4 & 1 \\
0.5 & 1 \\
0.6 & 1 \\
1 & 5 \\
1.1 & 2 \\
1.2 & 1 \\
1.3 & 1 \\
1.5 & 2 \\
1.6 & 2 \\
1.8 & 1 \\
1.9 & 2 \\
2.1 & 1 \\
2.2 & 2 \\
2.3 & 1 \\
2.4 & 3 \\
2.5 & 1 \\
2.6 & 1 \\
2.7 & 1 \\
2.9 & 1 \\
3 & 3 \\
3.1 & 4 \\
3.2 & 1 \\
3.3 & 6 \\
3.4 & 3 \\
3.5 & 2 \\
3.6 & 2 \\
3.8 & 2 \\
3.9 & 2 \\
4 & 13 \\
4.1 & 1 \\
4.2 & 2 \\
4.4 & 2 \\
4.5 & 1 \\
4.7 & 1 \\
4.8 & 1 \\
5 & 21 \\
5.1 & 5 \\
5.2 & 5 \\
5.3 & 1 \\
5.4 & 3 \\
5.5 & 1 \\
5.7 & 1 \\
5.8 & 2 \\
5.9 & 9 \\
6 & 13 \\
6.1 & 7 \\
6.4 & 1 \\
6.5 & 2 \\
6.7 & 3 \\
6.8 & 2 \\
6.9 & 5 \\
7 & 11 \\
7.1 & 1 \\
7.2 & 2 \\
7.3 & 1 \\
7.4 & 2 \\
7.5 & 4 \\
7.6 & 1 \\
7.7 & 3 \\
7.8 & 6 \\
7.9 & 9 \\
8 & 19 \\
8.1 & 4 \\
8.2 & 3 \\
8.3 & 5 \\
8.4 & 2 \\
8.5 & 4 \\
8.6 & 5 \\
8.7 & 6 \\
8.8 & 9 \\
8.9 & 15 \\
9 & 29 \\
9.1 & 4 \\
9.2 & 4 \\
9.3 & 2 \\
9.4 & 4 \\
9.5 & 13 \\
9.6 & 4 \\
9.7 & 17 \\
9.8 & 48 \\
9.9 & 90 \\
10 & 203 \\
\end{longtable}

@@

\includegraphics{compare_files/figure-pdf/cell-12-output-1.pdf}

@@

\includegraphics{compare_files/figure-pdf/cell-13-output-1.pdf}

@@

@@

\includegraphics{compare_files/figure-pdf/cell-21-output-1.pdf}

@@

\includegraphics{compare_files/figure-pdf/cell-22-output-1.pdf}

@@

\includegraphics{compare_files/figure-pdf/cell-25-output-1.pdf}

\includegraphics{compare_files/figure-pdf/cell-26-output-1.pdf}

@@

\includegraphics{compare_files/figure-pdf/cell-28-output-2.pdf}

@@

@@

\begin{verbatim}
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  5 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  5 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  5 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  5 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  5 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  5 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  5 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  5 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  5 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  5 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
 ** On entry to DLASCL parameter number  4 had an illegal value
\end{verbatim}

\includegraphics{compare_files/figure-pdf/cell-31-output-2.pdf}

@@

@@

\includegraphics{compare_files/figure-pdf/cell-37-output-1.pdf}

@@

\includegraphics{compare_files/figure-pdf/cell-38-output-1.pdf}

@@

@@

\includegraphics{compare_files/figure-pdf/cell-47-output-1.pdf}

>>>>

\caption{\label{fig-dis-comp}Histograms showing the Distance
Completeness of the Catalogs}

@@

\begin{table}

\caption{\label{tbl-dis-comp}Table showing the Completeness of the
Catalogs, per bin}

\subcaption{\label{tbl-dis-comp-1}HECATE}

\begin{tabular}{rrll}
\toprule
Bin Start & Bin End & Unique \% & Inner \%\\
\midrule
0 & 0 & 43\% & 57\%\\
0 & 1 & 93\% & 7\%\\
1 & 1 & 95\% & 5\%\\
1 & 2 & 98\% & 2\%\\
2 & 2 & 98\% & 2\%\\
2 & 2 & 95\% & 5\%\\
2 & 3 & 98\% & 2\%\\
3 & 3 & 96\% & 4\%\\
3 & 4 & 96\% & 4\%\\
4 & 4 & 95\% & 5\%\\
4 & 4 & 96\% & 4\%\\
4 & 5 & 90\% & 10\%\\
5 & 5 & 81\% & 19\%\\
5 & 6 & 86\% & 14\%\\
6 & 6 & 62\% & 38\%\\
6 & 6 & 58\% & 42\%\\
6 & 7 & 74\% & 26\%\\
7 & 7 & 71\% & 29\%\\
7 & 7 & 62\% & 38\%\\
7 & 8 & 64\% & 36\%\\
8 & 8 & 52\% & 48\%\\
8 & 9 & 71\% & 29\%\\
9 & 9 & 69\% & 31\%\\
9 & 9 & 77\% & 23\%\\
9 & 10 & 75\% & 25\%\\
10 & 10 & 73\% & 27\%\\
10 & 11 & 73\% & 27\%\\
11 & 11 & 83\% & 17\%\\
\bottomrule
\end{tabular}

\subcaption{\label{tbl-dis-comp-2}LCV}

\begin{tabular}{rrll}
\toprule
Bin Start & Bin End & Unique \% & Inner \%\\
\midrule
0 & 1 & 68\% & 32\%\\
1 & 2 & 50\% & 50\%\\
2 & 3 & 67\% & 33\%\\
3 & 4 & 80\% & 20\%\\
4 & 5 & 85\% & 15\%\\
5 & 6 & 79\% & 21\%\\
6 & 6 & 73\% & 27\%\\
6 & 7 & 83\% & 17\%\\
7 & 8 & 74\% & 26\%\\
8 & 9 & 72\% & 28\%\\
9 & 10 & 85\% & 15\%\\
10 & 11 & 78\% & 22\%\\
\bottomrule
\end{tabular}

\end{table}%

@@

\caption{\label{fig-type-comp}Histograms showing the Type Completeness
of the Catalogs}

@@

@@

\includegraphics{compare_files/figure-pdf/cell-15-output-1.pdf}

@@

\includegraphics{compare_files/figure-pdf/cell-20-output-1.pdf}

@@

\includegraphics{compare_files/figure-pdf/cell-23-output-1.pdf}

@@

\includegraphics{compare_files/figure-pdf/cell-24-output-1.pdf}

@@

@@

\includegraphics{compare_files/figure-pdf/cell-30-output-1.pdf}

\includegraphics{compare_files/figure-pdf/cell-30-output-2.pdf}

@@

\includegraphics{compare_files/figure-pdf/cell-31-output-1.pdf}

@@

@@

\includegraphics{compare_files/figure-pdf/cell-35-output-1.pdf}

@@

\includegraphics{compare_files/figure-pdf/cell-39-output-1.pdf}

@@

@@

\includegraphics{compare_files/figure-pdf/cell-46-output-1.pdf}

@@

\includegraphics{compare_files/figure-pdf/cell-49-output-1.pdf}
